Rigid fluid coupling

### 2022-02-22 manuscript/paper.tex
New rigid body collision case example from Amaro Junior 2019

  \title{Write title here}
  \author[IITB]{Adepu Dinesh \corref{cor1}}
  \ead{adepu.dinesh.a@gmail.com} \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in} \address[IITB]{Department of Aerospace
    Engineering, Indian Institute of Technology Bombay, Powai, Mumbai 400076}

@@

\section{Fluid mechanics}
\label{sec:fluid-mechanics}

\section{Rigid body dynamics}
\label{sec:rbd-dynamics}

\section{Rigid body contact model}
\label{sec:rbd-contact-model}

In the SPH literature there are a few ways to model the contact
between rigid bodies. Few ways to note are

\begin{itemize}
\item \citet{albano2016modelling} models using pure elastic impingement force
% Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
\item \citet{choidevelopment} models using DEM
\item \citet{zhan2020sph} uses hybrid contact model
\item \citet{} uses hybrid contact model
\end{itemize}
A  SPH  framework  for  dynamic interaction  between  soil  and  rigid  body  system  with  hybrid contact   metho

\section{Rigid fluid coupling}
\label{sec:rf-coupling}

\section{Results and discussion}
\label{sec:results}
\citet{wu2014two} has experimental solution to cube sinking and cube floating
in a tank.

\subsection{Cylinders collapsing under gravity in a tank}
\label{sec:cylinders-collapsing-dem}

This benchmark is taken from \citet{chen2019coupled} and
\citet{wang2019numerical}. This is to validate the rigid contact model.

Six layers of solid cylinders are stacked, and then suddenly released under
gravity. This is done by 2009 Zhang and Canelas 2016.

\subsection{A block of density 2000 freely falling in to a steady tank}
\label{sec:2000-density-inside-tank}

This benchmark is taken from \citet{qiu20173d}.

A water tank of 150 $mm$ $\times$ 140 $mm$ $\times$ 140 $mm$ and the water
depth in the tank was 131 $mm$. The cube with a side length of 20 $mm$. The
density of the cube is 2120 $kg m^{-3}$. The cube is placed half way before
the release into the fluid. The spring stiffness coefficient of 1 $\times$
$10^{5}$ $N m^{-1}$.

\subsection{A block of density $800.52$ floating in a steady tank}
\label{sec:800-density-floating}

This benchmark is taken from \citet{qiu20173d}, \citet{wang2019numerical}.

A water tank of 150 mm $\times$ 140 mm $\times$ 140 mm and the water depth in
the tank was 52 $mm$. A rectangular wooden block (with a width of 48 mm,
length of 49 mm, height 24mm) whose density is 800.52 kg$m^{-1}$ is
released from the bottom of the tank. We compare the vertical displacement of
the center of mass of the cube.

@@

This benchmark is taken from \citet{wang2019numerical}.

Here we simulate a solid body transport in a dam break.

\subsection{Dam break with multiple body transport}
\label{sec:dam-break-with-multiple-body-transport}

This benchmark is taken from \citet{wang2019numerical}.

Here we simulate a transport of multiple bodies in a dam break.

\subsection{Cylinders in water collapsed under gravity}
\label{sec:cylinders-in-water-collapsed-under-gravity}

This benchmark is taken from \citet{chen2019coupled}.

Here we simulate a collapse of cylinders submerged in a water under gravity.

\subsection{Single cube transport in 3d dam break with out any obstructions}
\label{sec:single-cube-transport-in-3d-dam-break-with-out-any-obstructions}

This benchmark is taken from \citet{ji2019coupled}.

A single body transport under 3d dam break. Here we don't have any
obstructions. This is done in Canelas 2016 DCDEM paper. This is different from
Amicarelli paper.

\subsection{Three cube transport in 3d dam break with out any obstructions}
\label{sec:three-cube-transport-in-3d-dam-break-with-out-any-obstructions}

This benchmark is taken from \citet{ji2019coupled}.

Three cubes transport under 3d dam break. Here we don't have any obstructions.
This is done in Canelas 2016 DCDEM paper. This is different from Amicarelli
paper.

>>>>

  \title{Rigid fluid coupling}
  \author[IITB]{Adepu Dinesh \corref{cor1}}
  \ead{adepu.dinesh.a@gmail.com} \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in} \address[IITB]{Department of Aerospace
    Engineering, Indian Institute of Technology Bombay, Powai, Mumbai 400076}

@@

\section{Governing equations}
\label{sec:fluid-mechanics}

\section{CTVF formulation}
\label{sec:ctvf-equations}

\section{SPH discretization}
\label{sec:sph-fluid-equations}

\section{Rigid body dynamics}
\label{sec:rbd}

\section{How to handle rigid fluid coupling}
\label{sec:rfc}

\section{Collision between rigid bodies}
\label{sec:contact-force}

\citet{chen2019coupled} has damping model. Also he mentioned the parameters
required in stack of cylinders example.

% \todoin{
% \begin{itemize}
% \item \citet{albano2016modelling} models using pure elastic impingement force
% % Development of the Resolved Fluid-Solid SPH Coupling using Rigid Body Dynamics
% \item \citet{choidevelopment} models using DEM
% \item \citet{zhan2020sph} uses hybrid contact model
% \end{itemize}
% A SPH framework for dynamic interaction between soil and rigid body system
% with hybrid contact method}

\section{Results and discussion}
\label{sec:results}

\subsection{Rigid block of different densities allowed to sink into water}
\label{sec:rigid-block-diff}

\subsection{A 2d and 3d rigid body sliding}
\label{sec:rigid-body-sliding}

\subsection{Bouncing cube on a wall under gravity}
\label{sec:bouncing-cube}

\subsection{Stack of cylinders}
\label{sec:stack-of-cylinders}

\subsection{A test to check the conservation properties of rigid body}
\label{sec:conservation-of-rb-properties}

\subsection{Debris dam break flow}
\label{sec:debris-dam-break-canelas}

\subsubsection{Case I}
\label{sec:debris-dam-break-canelas-case-I}

\subsubsection{Case II}
\label{sec:debris-dam-break-canelas-case-II}

\subsubsection{Case III}
\label{sec:debris-dam-break-canelas-case-III}

@@

\citet{wang2019numerical}

\subsection{Dam break with multiple bodies transport}
\label{sec:dam-break-with-multiple-bodies-transport}
\citet{wang2019numerical}

\subsection{Cylinders in water collapsed under gravity}
\label{sec:cylinders-collapse-in-water}
\citet{chen2019coupled}
